Commutative Character Sheaves on smooth group schemes over finite fields

### 2016-02-23 followup.tex
Fixed notation in Section 4.

@@

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
Let us refer to the types arising in this manner as {\it Yu types}.
%In this section we show that every Yu type is geometrizable.
% in a sense which will be made clear below.
%
A Yu type is then a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, constructed in a certain way. 
%
In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
%from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius. 
Unfortunately, the proof of this statement,  which is Proposition~\ref{prop:geotypes}, is quite technical, so the proof must be delayed to Section~\ref{ssec:geotypes}, after reviewing the types and models developed by Yu.

\subsection{Quasicharacters of smooth group schemes over $p$-adic fields}

@@

Set $S = \Spec{\OK}$ and $S_n = \Spec{\OK/\mathfrak{m}^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$, and $n$ is a positive integer $n$.
Let $\underline{G}$ be a smooth group scheme over $\OK$.
Let $G_n$ be the Greenberg transform of $\underline{G} \times_{S} S_n$.
Then $G_n$ is a smooth group scheme over $\Fq$ and 
\[
G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n),
\]
canonically.
%
Let $G$ be the Greenberg transform of $\underline{G}$.
Then $G$ is a group scheme over $\Fq$ and 
\[
G(\Fq) = \underline{G}(\OK)
\]
canonically.

\begin{proposition}\label{prop:quasicharacters}
Let $\underline{G}$ be a smooth group scheme over $\OK$.
Let $\chi : \underline{G}(\OK) \to \EEx$ be a quasicharacter/continuous linear character. 
Then there is a Weil sheaf $\cs{L}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \chi$. \todo{Missing proof}
\end{proposition}

\begin{proof}
\end{proof}

@@

%For use in the next section, we recall some basic facts about the Heisenberg-Weil representation.

Let $V$ be a finite-dimensional vector space over a finite field $\Fq$ equipped with a symplectic paring $\langle\ ,\ \rangle : V\times V \to C$, where $C$ is a one-dimensional vector space over $\Fq$.
Then $V$ is even-dimensional and we may pick a `Lagrangian splitting' $V = U \oplus W$ such that $\langle v,v' \rangle = (u,w') - (u',w)$ for $v=(u,w)$ and $v'=(u',w')$.
Let $V^\sharp$ be the Heisenberg group determined by $(C, \langle\ ,\ \rangle)$.
Then $V^\sharp$ is a split extension of $V$ by $C$.
\[
\begin{tikzcd}
\ &&& U \arrow{d} &\\
1 \arrow{r} & C \arrow{r} & V^\sharp \arrow{r} & \arrow[bend right]{l} V \arrow[bend right]{u} \arrow[bend left]{d} \arrow{r} & 1\\
1 \arrow{r} & \arrow[equals]{u} C \arrow{r} & \arrow[bend right]{l}  A \arrow{u} \arrow{r} & \arrow[bend right]{l}  W \arrow{u} \arrow{r} & 1 
\end{tikzcd}
\]

Let $\psi : C \to \EEx$ be an additive character and let $\omega$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : C \to \EEx$. 
Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$;
this group acts on $V^\sharp$.
Extend $\psi$ to $\psi_A : A \to \EEx$ in the obvious way. 
Then $\omega \ceq \operatorname{Ind}_A^{V^\sharp}(\psi_A)$ is called the Heisenberg representation of $V^\sharp$.

Observe that $\Sp(V)$ acts on $V^\sharp$.
The Heisenberg representation determines a representation $\pi_{\omega}$ of $\Sp(V)$ with the same representation space as $\omega$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\omega(g)$ determines an isomorphism of representations $\omega^g \to \omega$, through the Egorov identity \cite{Gurevich-Hadani:geometric_Weil}*{(1.3.1)}.
Let $W = \pi_\omega \ltimes \omega$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega$ and $\pi_\omega$.

\begin{conjecture}\label{conj:Jacobi}
For $V$, $C$, $\langle\, , \ \rangle$, $\psi$ and $W$ as above, there is a Weil sheaf $\cs{W}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{W}} = \trace(W)$.
\end{conjecture}

@@

Every Yu type $(\,^\circ K,\,^\circ \rho)$ may be constructed directly from the following information, derived from a Yu datum:
\begin{enumerate}
\item[(0)] a sequence of compact groups 
\[
\,^\circ K^0 \subseteq \,^\circ K^1 \subseteq \cdots \subseteq \,^\circ K^d= \,^\circ K;
\]
\item[(1)] a continuous representation $\varrho$ of $\,^\circ K^0$;
\item[(2)] a quasicharacter $\varphi^i : \,^\circ K^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
The representations $(\varrho, \varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\,^\circ\rho_i$ of $\,^\circ K^i$, for $i=0, \ldots, d-1$, such that $\,^\circ\rho_0 = \varrho$ and $\,^\circ\rho_d = \,^\circ\rho$.

Since we will need some facts about this construction, we review some further detail here.
First, Yu introduces compact groups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that 
\[
\,^\circ K^i = J^0\cdots J^{i}
\]
and a natural action of $\,^\circ K^i$ on $J^{i+1}$, for $i=0, \ldots d-1$, defining the groups
\[
\,^\circ K^i \ltimes J^{i+1}.
\]
He then introduces the following quotients of $J^{i+1}$ and $\,^\circ K^i$, for $i=0, \ldots d-1$.
\begin{enumerate}
\item[(Q.1)] A quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
\end{enumerate}
The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : C_{i+1} \to \EEx$.
\begin{enumerate}
\item[(Q.2)] A quotient $J^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $C_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
\end{enumerate}
In fact, the quotient $J^{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J^{i+1} \to H^{i+1}$ and an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:construction}*{}.
\begin{enumerate}
\item[(Q.3)] A quotient $\,^\circ f_{i+1} : \,^\circ K^i \to \Sp(V_{i+1})$, such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $\,^\circ K^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}.
\end{enumerate}
Taken together, these quotients define another quotient:
\begin{enumerate}
\item[(Q)] A quotient $h_{i+1} : \,^\circ K^i \ltimes J^{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
\[
\begin{tikzcd}
1 \arrow{r} & J^{i+1} \arrow{d} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d}{h_{i+1}} \arrow{r} & \,^\circ K^i \arrow{r} \arrow{d}{\,^\circ f_i} & 1\\ 
1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
\end{tikzcd}
\]
\end{enumerate}

The representations $\,^\circ \rho_i$ are defined recursively. Set $\,^\circ \rho_0 = \varrho$.
Suppose $i=0, \ldots, d-1$.
The key to defining the representation $\,^\circ\rho_{i+1}$ from $\,^\circ \rho_i$ is the following diagram.
\begin{equation}\label{eq:semiprod}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & \,^\circ K^i \arrow{r} & 1\\
&& \,^\circ K^{i+1} \arrow{d}{} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\,^\circ K^i \ltimes J^{i+1}$.
Write $\inf(\,^\circ\rho_i \otimes \varphi^i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$. 
Consider the representation
\begin{equation}\label{eq:tensor}
\,^0{\tilde\rho}_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi^i)
\end{equation}
of $\,^\circ K^i \ltimes J^{i+1}$.
By construction, the character of this representation satisfies
\begin{equation}\label{eq:tilderho}
\trace(\,^0{\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\,^\circ\rho_i)(p_i(y))\ \varphi^i(p_i(y))
\end{equation}
for $y \in \,^\circ K^i \ltimes J^{i+1}$.
By \cite{yu:01a}*{}, the representation $\,^0{\tilde\rho}_{i+1}$ of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$ so $\,^0{\tilde\rho}_{i+1}$ descends to $\,^\circ K^{i+1}$. 
This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi^d$, so this can't be quite right.}
%The character of $\,^\circ \rho_d$ on $\,^\circ K^d = \,^\circ K = J^0 \cdots J^d$ satisfies
%\[
%\trace(\,^\circ \rho)(k_0 \cdots k_d) = \varrho(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
%\]
%for $k_i\in J^i$.

@@

\begin{enumerate}
\item[(K)]
By \cite{yu:models}*{Prop 10.2} there is a sequence  
\[
\underline{G}^0 \to \underline{G}^1 \to \cdots \to \underline{G}^d = \underline{G}
\]
of morphisms of affine smooth group schemes of finite type over $\OK$ such that, on $\OK$-points it gives the sequence $\,^\circ K^0 \subseteq \,^\circ K^1 \subseteq \cdots \subseteq \,^\circ K^d= \,^\circ K$ above.
\item[(J)]
As explained in \cite{yu:03a}*{\S 10.4}, for each $i=0,\ldots d$, there is morphism of affine smooth group schemes of finite type over $\OK$ 
\[
\underline{J}^i \to \underline{G}
\] 
such that $\underline{J}^i(\OK) = J^i$ as a subgroup of $\,^\circ K$ and such that the image of the $\OK$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $\,^\circ K^i$, for $i=0, \ldots , d$.
\item[(S)]
There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $\OK$ so that the group
\[
\underline{G}^i \ltimes \underline{J}^{i+1}
\]
has $\OK$-points
\[
(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) = \,^\circ K^i \ltimes J^{i+1}.
\]
\end{enumerate}

@@

Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $U^{i+1}_\Fq$, where $U^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to U^{i+1}_\Fq$ of algebraic groups. Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
\[
\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to U^{i+1}_{\Fq}(\Fq) = V_{i+1}.
\]
Likewise, the Heisenberg p-group $H^{i+1}$ group may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
\[
\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
\]
Finally, the group homomorphism $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
\[
\underline{G}^{i}(\OK) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
\]

@@

Consider the following diagram of smooth group schemes over $\OK$ and compare with \eqref{eq:semiprod}.
\begin{equation}\label{eq:pimodel}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \underline{G}^{i}\times_{\underline{G}} \underline{J}^{i+1}\arrow{d} && \\
1 \arrow{r} & \underline{J}^{i+1} \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{d} \arrow{r} & \underline{G}^i \arrow{r} & 1\\
&& \underline{G}^{i+1} \arrow{d} && \\
&& 1 &&
\end{tikzcd}
\end{equation}

>>>>

In the remainder of this section we use Theorem~\ref{thm:geo} to geometrize the representation $\rho$ of $C$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\rho)$.
The proof of this statement is quite technical, so it must be delayed to Section~\ref{ssec:geotypes}, after reviewing types in Section~\ref{ssec:types} and models Section~\ref{ssec:models} developed by Yu, for which we must also review some facts about the Heisenberg-Weil representation in Section~\ref{ssec:Jacobi}, and also make a conjecture about the geometrization of that representation, Conjecture~\ref{conj}.

@@

\subsection{Quasicharacters of smooth group schemes over certain henselian traits}

@@

Let $R$ be a complete discrete valuation ring with maximal ideal $\mathfrak{m}$ and perfect residue field $\Fq$. 
Then $\Spec{R}$ is a henselian trait.
Let $\underline{G}$ be a smooth group scheme over $R$.
Here we shall use  \cite{BGA} for the definition and fundamental properties of the Greenberg transform.
Let $G$ be the Greenberg transform of $\underline{G}$; then $G$ is a group scheme over $\Fq$ and 
\[
G(\Fq) = \underline{G}(R)
\]
canonically.

\begin{proposition}\label{prop:quasicharacters}
With notation as above, suppose $\Fq$ is a finite field.
For every quasicharacter/continuous linear character $\chi : \underline{G}(S) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} = \trace \chi.\] \end{proposition}

\begin{proof}
Set $S = \Spec{R}$ and, for every non-negative integer, set $S_n = \Spec{R/\mathfrak{m}^{n+1}}$.
 Then $G_n \ceq \Gr_n^{R}(\underline{G})$, the Greenberg transform of $\underline{G} \times_{S} S_n$, is a smooth group scheme over $\Fq$ and 
\[
G_n(\Fq) = \underline{G}(S_n),
\]
canonically.
\end{proof}

@@

For use below, we recall some basic facts about the Heisenberg-Weil representation and make a conjecture about the geometrization of these representations.
We refer the reader to \cite{BS} for more detail.

Let $V$ be a finite-dimensional vector space over a finite field $\Fq$ equipped with a symplectic paring $\langle\ ,\ \rangle : V\times V \to Z$, where $Z$ is a one-dimensional vector space over $\Fq$.
Let $V^\sharp$ be the Heisenberg group determined by $(Z, \langle\ ,\ \rangle)$.
Then $V^\sharp$ is a split extension of $V$ by $Z$.
Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$; this group acts on $V^\sharp$.
Then  is the Jacobi group. 
From the construction above, it is clear that $\Sp(V)\ltimes V^\sharp$ may be viewed as the $\Fq$-points of an algebraic group over $\Fq$; we will refer to that algebraic group as the Jacobi group.

Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : Z \to \EEx$. 
The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
% through the Egorov identity \cite{Gurevich-Hadani:geometric_Weil}*{(1.3.1)}.\todo{Find better reference.}
Let $W_\psi = \pi_\psi \ltimes \omega_\psi$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega_\psi$ and $\pi_\psi$.

\begin{conjecture}\label{conj:Jacobi}
%Notation as above.
There is an equivariant Weil sheaf $\cs{W}_\psi$ on the Jacobi group such that 
\[
\trFrob{\cs{W}_\psi} = \trace(W_\psi).
\]
\end{conjecture}

\iffalse
Pick a Lagrangian splitting $V = U \oplus U'$. 
%such that $\langle v,v' \rangle = (u,w') - (u',w)$ for $v=(u,w)$ and $v'=(u',w')$.
Let $B \to V^\sharp$ be the subgroup defined by the diagram below.
\[
\begin{tikzcd}
\ &&& U' \arrow{d} &\\
1 \arrow{r} & Z \arrow{r} & V^\sharp \arrow{r} & \arrow[bend right]{l} V \arrow[bend right]{u} \arrow[bend left]{d} \arrow{r} & 1\\
1 \arrow{r} & \arrow[equals]{u} Z \arrow{r} & \arrow[bend right]{l}  B \arrow{u} \arrow{r} & \arrow[bend right]{l}  U \arrow{u} \arrow{r} & 1 
\end{tikzcd}
\]
Extend $\psi$ to $\psi_B : B \to \EEx$ in the obvious way. 
Then $\omega \ceq \operatorname{Ind}_A^{V^\sharp}(\psi_A)$ is called the Heisenberg representation of $V^\sharp$.
\fi

@@

For the rest of Section~\ref{sec:types}, $K$ is a $p$-adic field.

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
Let us refer to the types arising in this manner as {\it Yu types}.
%In this section we show that every Yu type is geometrizable.
% in a sense which will be made clear below.
%
A Yu type is then a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
\begin{enumerate}
\labitem{Y0}{Y0} a sequence of compact groups $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$;
\labitem{Y1}{Y1} a continuous representation $\rho^0$ of $C^0$;
\labitem{Y2}{Y2} a quasicharacter $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
The representations $(\rho^0, \varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho^d = \rho$.

Since we will need some facts about this construction, we review some further detail here.
First, Yu introduces 
\begin{enumerate}
\labitem{Y3}{Y3}
compact groups $J^i\subset C$, for $i=0, \ldots d$, such that 
$
C^i = J^0\cdots J^{i}
$ 
and, for $i=0, \ldots d-1$, a natural action of $C^i$ on $J^{i+1}$ defining the groups $C^i \ltimes J^{i+1}$.
\begin{equation}\label{eq:semiprod}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && C^{i}\cap J^{i+1}\arrow{d} && \\
1 \arrow{r} & J^{i+1} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} & 1\\
&& C^{i+1} \arrow{d}{} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
\end{enumerate}
%He then introduces the following quotients of $J^{i+1}$ and $C^i$, for $i=0, \ldots d-1$.
Next, Yu uses this to define a group homomorphism (in fact, a quotient) 
$
J^{i+1} \to V_{i+1}
$
where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : C_{i+1} \to \EEx$.
%\labitem{Q2}{Q2} 
%\item 
This, in turn, is used to define a map
$
J^{i+1} \to V_{i+1}^\sharp,
$
where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $C_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
In fact, the quotient $J^{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J^{i+1} \to H^{i+1}$ and an isomorphism 
$
j_{i+1} : H^{i+1} \to V_{i+1}^\sharp,
$
where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:construction}*{}.
%\labitem{Q3}{Q3} 
%\item
Finally, Yu constructs 
$
f_{i+1} : C^i \to \Sp(V_{i+1}),
$
such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}.
Taken together, this defines
%\end{enumerate}
\begin{enumerate}
\labitem{Y4}{Y4}  a group homomorphism $h_{i+1} : C^i \ltimes J^{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
\[
\begin{tikzcd}
1 \arrow{r} & J^{i+1} \arrow{d} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} \arrow{d}{f_i} & 1\\ 
1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
\end{tikzcd}
\]
\end{enumerate}

We can now recall how Yu uses all this to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho^d)$.
The representations $\rho^i$ are defined recursively. 
For the base case $i=0$, the representation $\rho^0$ is part of the datum; see \ref{Y1} above.
%The key to defining the representation $\rho^{i+1}$ from $\rho^i$ is \ref{Y3}, above.
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J^{i+1}$.
Write $\inf(\rho^i \otimes \varphi^i)$ for the representation of $C^i \ltimes J^{i+1}$ obtained by pulling back $\rho^i$ along $C^i \ltimes J^{i+1} \to C^i$. 
Consider the representation
\begin{equation}\label{eq:tensor}
\rho_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\rho^i \otimes \varphi^i)
\end{equation}
of $C^i \ltimes J^{i+1}$.
%By construction, the character of this representation satisfies
%\begin{equation}\label{eq:tilderho}
%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\rho^i)(p_i(y))\ \varphi^i(p_i(y))
%\end{equation}
%for $y \in C^i \ltimes J^{i+1}$.
By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J^{i+1}$ is trivial on $C^{i}\cap J^{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$. 
This defines the representation $\rho^{i+1}$ of $C^{i+1}$. \todo{I didn't use $\varphi^d$, so this can't be quite right.}
This completes the recursive definition and this determines $\rho^d = \rho$, which is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
%The character of $\rho^d$ on $C^d = C = J^0 \cdots J^d$ satisfies
%\[
%\trace(\rho)(k_0 \cdots k_d) = \rho^0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
%\]
%for $k_i\in J^i$.

@@

As a step toward geometrizing the type $(C,\rho)$, we now recall some results from \cite{yu:models}.

%\begin{enumerate}
%\labitem{M1}{M1}
By \cite{yu:models}*{Prop 10.2} there is a sequence  
\[
\underline{G}^0 \to \underline{G}^1 \to \cdots \to \underline{G}^d = \underline{G}
\]
of morphisms of affine smooth group schemes of finite type over $\OK$ such that, on $\OK$-points it gives the sequence $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$ above.
Indeed, this is the main result of \cite{yu:models}.

%\labitem{M2}{M2}
As explained in \cite{yu:03a}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $\OK$ 
\[
\underline{J}^i \to \underline{G},
\] 
for each $i=0,\ldots d$, such that $\underline{J}^i(\OK) = J^i$ as a subgroup of $C$ and such that the image of the $\OK$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
%\labitem{M3}{M3}
There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $\OK$ so that the group scheme
\[
\underline{G}^i \ltimes \underline{J}^{i+1}
\]
gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) = C^i \ltimes J^{i+1}$
%\end{enumerate}

@@

Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}_\Fq$, where $V^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to V^{i+1}_\Fq$ of algebraic groups. Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
\[
\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}_\Fq(\Fq) = V_{i+1}.
\]
Likewise, the Heisenberg $p$-group $H^{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
\[
\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
\]
Finally, the group homomorphism $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
\[
\underline{G}^{i}(\OK) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
\]

@@

We may now revisit the ingredients in the construction of the representation $\rho$ of $\underline{G}(\OK)$ along the lines indicated by Yu and recalled in Section~\ref{ssec:review}.
\begin{enumerate}
\labitem{M0}{M0}
The compact groups $C^i$ have been replaced by the smooth group schemes $\underline{G}^i$.
\labitem{M1}{M1}
The continuous representation $\rho^0$ of $C^0$ is a representation of $\underline{G}^0(\OK)$ obtained by inflation along $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$ from a representation $\rho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
In fact, $\rho_0$ is itself obtained by pulling back a representation $\rho_0^\reductive$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
\labitem{M2}{M2} The quasicharacters $\varphi^i$ are quasicharacters of $\underline{G}^i(\OK)$, for $i=0, \ldots d$.
\labitem{M3}{M3}
Diagram \eqref{eq:semiprod} is now replaced by the following diagram of smooth group schemes over $\OK$.
\begin{equation}\label{eq:pimodel}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \underline{G}^{i}\times_{\underline{G}} \underline{J}^{i+1}\arrow{d} && \\
1 \arrow{r} & \underline{J}^{i+1} \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{d} \arrow{r} & \underline{G}^i \arrow{r} & 1\\
&& \underline{G}^{i+1} \arrow{d} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
\labitem{M4}{M4}
The representation $h_{i+1}^*(W_{i+1})$ appearing in \ref{Y4} is now obtained by pulling back a representation along 
\[
(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
\]
Let $w_{i+1}$ be that representation of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq) = (\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq)(\Fq)$. 
Then $w_{i+1}$ is itself obtained by pulling back the representation $W_{i+1}$ along the $\Fq$-points of the quotient
\[
\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq \to 
\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp.
\]
\end{enumerate}

Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:models} concludes with the following provocative observation, which we have just revisited.
\begin{quotation}
{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
 the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$. These results suggest that algebraic geometry and group schemes should play an
important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
\end{quotation}
%In fact, Yu's description of how to assemble $\rho$ from $(\rho^0, \varphi^0, \ldots , \varphi^d)$ is slightly different, but equivalent, to what we have done here \cite{Yu:models}*{}.
